Articles of Association of London Hackspace Ltd

### 2015-12-01 constitution/articles-body.tex
Remove hearing requirement for removal of membership
Fixes #2

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. A resolution to remove a
    member from membership may only be passed if:
    \begin{enumerate}
    \item
      the member has been given at least twenty-one days' notice in
      writing of the meeting of the directors at which the resolution
      will be proposed and the reasons why it is to be proposed;
    \item
      the member or, at the option of the member, the member's
      representative (who need not be a member of the association) has been
      allowed to make representations to the meeting.
    \end{enumerate}
  \end{enumerate}

>>>>

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. Such a resolution may only be
    passed after the Board has exhausted all other options under the
    Grievance Procedure.
\end{enumerate}
